---
title: "Lesion manuscript - Rabbit model VPCs for all drugs"
author: "Anu Patel"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

> Switched IDV for DLM caseum VPC to TIME instead of TAD
> Switched IDV for RBT caseum VPC to TIME
> Switched IDV for RZL lung, cell, and caseum VPCs to TIME

# Set Up
```{r setup, include=FALSE}
library(vpc)
library(xpose)
library(xpose4)
library(grid)
library(gridExtra)
library(ggplot2)
library(reshape)

# master path
WD <- "/Volumes/savic/translational_team/aebustion/lesion_vpcs/"
```

# Plasma VPCs (no metabolite)
> BTZ-043, CFZ, DLM, GSK-286, GSK-656 (GFB), GTX, INH, mCLB-073 (TBD-11), MXF, OPC-167832 (QBD), PMD, PZA, RBT, RIF, RPT

## Gather info for loop
```{r}
drugs <- c("BTZ-043", "CFZ", "GSK-286", "GFB", 
           "GTX", "INH", "TBD-11", 
           "MXF", "QBD", "PMD", "PZA", 
           "RIF", "RPT")

wd_values <- c("BTZ043/Plasma/", "CFZ/Plasma/", "GSK286/Plasma/", "GSK656/Plasma/", 
               "GTX/Plasma/", "INH/Plasma/", "mCLB073/Plasma/",
               "MXF/Plasma/", "OPC167832/Plasma/", "PMD/Plasma/", "PZA/Plasma/",
               "RIF/Plasma/", "RPT/Plasma/")

runno_values <- c("004c", "11b", "30", "100", 
                  "121_CLint", "07",  "20",
                  "31", "9", "13", "04",
                  "02", "6")
```

## Run VPCs
```{r}
p_plasma_plot_list <- list() # create an empty list to store the plots

for (i in seq_along(drugs)) { # to access corresponding elements of each list for each loop
  drug <- drugs[i]
  wd <- wd_values[i]
  runno <- runno_values[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
p_plasma <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                             wd,
                                            'run', 
                                             runno, 
                                            'vpc-idv'),
                         obs_cols = list(idv = "TAD"),
                         sim_cols = list(idv = "TAD"),
                         bins = "pretty",
                         pred_corr = F,
                       # logy = T,
                         show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
# scale_y_log10() +
  labs(title = drug, subtitle = "Plasma",
       x = "Time after dose (h)",
       y = "Concentration (mg/L)")

p_plasma_plot_list[[i]] <- p_plasma # store each plot in the list
}

for (i in seq_along(p_plasma_plot_list)) { # display each plot
  print(p_plasma_plot_list[[i]])
}
```

### DLM, RBT, RZL
```{r}
drugs <- c("DLM", "RBT", "RZL")
wd_values <- c("DLM/Plasma/", "RBT/Plasma/", "RZL/Plasma/")
runnos <- c("29", "15", "46")

p_plasma_dlm_rbt_rzl_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno <- runnos[i]
  
p_plasma_dlm_rbt_rzl <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                                         wd,
                                                        'run', 
                                                         runno, 
                                                        'vpc-idv'),
                         obs_cols = list(idv = "TAD"),
                         sim_cols = list(idv = "TAD"),
                         bins = "pretty",
                         pred_corr = F,
                         show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = drug, subtitle = "Plasma",
       x = "Time after dose (h)",
       y = "Concentration (mg/L)")

p_plasma_dlm_rbt_rzl_list[[i]] <- p_plasma_dlm_rbt_rzl
}

for (i in seq_along(p_plasma_dlm_rbt_rzl_list)) {
  print(p_plasma_dlm_rbt_rzl_list[[i]])
}
```

# Lesion VPCs (no metabolite)
> BTZ-043, CFZ, DLM, GSK-286, GSK-656 (GFB), GTX, INH, mCLB-073 (TBD-11), MXF, OPC-167832 (QBD), PMD, PZA, RBT, RIF, RPT, RZL

## Gather info for loop
```{r}
drugs <- c("BTZ-043", "CFZ", "GSK-286", "GFB", 
           "GTX", "INH", "TBD-11", 
           "MXF", "QBD", "PMD", "PZA", 
           "RIF", "RPT")

wd_values <- c("BTZ043/", "CFZ/", "GSK286/", "GSK656/", 
               "GTX/", "INH/", "mCLB073/", 
               "MXF/", "OPC167832/", "PMD/", "PZA/", 
               "RIF/", "RPT/")

runnos_lung <- c("L01p_004c", "L01b", "L14", "L01c", 
                 "121_1a_linear_error", "L01", "L08", 
                 "54b_p",  "L02_pfix", "L01", "L10",
                 "46_02", "11")

runnos_cell <- c("L02p_004c", "L02b", "L13", "L02d", 
                 "121_2a_linear_error", "L02", "L07", 
                 "64", "L01_pfix", "L02a", "L13", 
                 "52_02", "18")

runnos_case <- c("L04m3pfix_004c_2", "L06g", "L11", "L03d", 
                 "121_3a_linear_error", "L08d_a", "L03", 
                 "84", "L03_p", "L03b", "L17", 
                 "53_02", "19")
```

## Run Lung VPCs
```{r}
p_lung_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_lung <- runnos_lung[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
p_lung <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                           wd,
                                          'Lung/',
                                          'vpc_',
                                          'run', 
                                           runno_lung),
                       obs_cols = list(idv = "TAD"),
                       sim_cols = list(idv = "TAD"),
                       bins = "pretty",
                       pred_corr = F,
                       show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Lung",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

p_lung_plot_list[[i]] <- p_lung
}

for (i in seq_along(p_lung_plot_list)) {
  print(p_lung_plot_list[[i]])
}
```

### DLM, RBT
```{r}
drugs <- c("DLM", "RBT")
wd_values <- c("DLM/Lung/", "RBT/Lung/")
runnos_lung <- c("L01b", "L01")

p_lung_dlm_rbt_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_lung <- runnos_lung[i]
  
p_lung_dlm_rbt <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                                   wd,
                                                   'vpc_',
                                                   'run', 
                                                   runno_lung),
                           obs_cols = list(idv = "TAD"),
                           sim_cols = list(idv = "TAD"),
                           bins = "pretty",
                           pred_corr = F,
                           show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Lung",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

p_lung_dlm_rbt_list[[i]] <- p_lung_dlm_rbt
}

for (i in seq_along(p_lung_dlm_rbt_list)) {
  print(p_lung_dlm_rbt_list[[i]])
}
```

### RZL (using TIME instead of TAD)
```{r}
drugs <- c("RZL")
wd_values <- c("RZL/Lung/")
runnos_lung <- c("L22")

p_lung_rzl_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_lung <- runnos_lung[i]
  
p_lung_rzl <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                               wd,
                                               'vpc_',
                                               'run', 
                                               runno_lung),
                           obs_cols = list(idv = "TIME"),
                           sim_cols = list(idv = "TIME"),
                           bins = "pretty",
                           pred_corr = F,
                           show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(24,168,48)) +
  labs(title = "", subtitle = "Lung",
       x = "Time (h)",
       y = "Concentration (mg/kg)")

p_lung_rzl_list[[i]] <- p_lung_rzl
}

for (i in seq_along(p_lung_rzl_list)) {
  print(p_lung_rzl_list[[i]])
}
```

```{r}
drugs <- c("BTZ-043", "CFZ", "GSK-286", "GFB", 
           "GTX", "INH", "TBD-11", 
           "MXF", "QBD", "PMD", "PZA", 
           "RIF", "RPT")

wd_values <- c("BTZ043/", "CFZ/", "GSK286/", "GSK656/", 
               "GTX/", "INH/", "mCLB073/", 
               "MXF/", "OPC167832/", "PMD/", "PZA/", 
               "RIF/", "RPT/")

runnos_cell <- c("L02p_004c", "L02b", "L13", "L02d", 
                 "121_2a_linear_error", "L02", "L07", 
                 "64", "L01_pfix", "L02a", "L13", 
                 "52_02", "18")
```

## Run Cell VPCs
```{r}
#### re-run original drug and run list names first

p_cell_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_cell <- runnos_cell[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
p_cell <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                           wd,
                                           'Cell/',
                                           'vpc_',
                                           'run', 
                                            runno_cell),
                       obs_cols = list(idv = "TAD"),
                       sim_cols = list(idv = "TAD"),
                       bins = "pretty",
                       pred_corr = F,
                       show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Cellular Lesion",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

p_cell_plot_list[[i]] <- p_cell
}

for (i in seq_along(p_cell_plot_list)) {
  print(p_cell_plot_list[[i]])
}
```

### DLM, RBT
```{r}
drugs <- c("DLM", "RBT")
wd_values <- c("DLM/Cell/", "RBT/Cell/")
runnos_cell <- c("L02g", "L02")

p_cell_dlm_rbt_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_cell <- runnos_cell[i]
  
p_cell_dlm_rbt <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                                   wd,
                                                   'vpc_',
                                                   'run', 
                                                   runno_cell),
                         obs_cols = list(idv = "TAD"),
                         sim_cols = list(idv = "TAD"),
                         bins = "pretty",
                         pred_corr = F,
                         show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Cellular Lesion",
       x = "Time after dose (h)",
       y = "Concentration (mg/L)")

p_cell_dlm_rbt_list[[i]] <- p_cell_dlm_rbt
}

for (i in seq_along(p_cell_dlm_rbt_list)) {
  print(p_cell_dlm_rbt_list[[i]])
}
```

### RZL (using TIME instead of TAD)
```{r}
drugs <- c("RZL")
wd_values <- c("RZL/Cell/")
runnos_cell <- c("L23")

p_cell_rzl_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_cell <- runnos_cell[i]
  
p_cell_rzl <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                               wd,
                                               'vpc_',
                                               'run', 
                                               runno_cell),
                         obs_cols = list(idv = "TIME"),
                         sim_cols = list(idv = "TIME"),
                         bins = "pretty",
                         pred_corr = F,
                         show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(24,168,48)) +
  labs(title = "", subtitle = "Cell",
       x = "Time (h)",
       y = "Concentration (mg/L)")

p_cell_rzl_list[[i]] <- p_cell_rzl
}

for (i in seq_along(p_cell_rzl_list)) {
  print(p_cell_rzl_list[[i]])
}
```

```{r}
drugs <- c("BTZ-043", "CFZ", "GSK-286", "GFB", 
           "GTX", "INH", "TBD-11", 
           "MXF", "QBD", "PMD", "PZA", 
           "RIF", "RPT")

wd_values <- c("BTZ043/", "CFZ/", "GSK286/", "GSK656/", 
               "GTX/", "INH/", "mCLB073/", 
               "MXF/", "OPC167832/", "PMD/", "PZA/", 
               "RIF/", "RPT/")

runnos_case <- c("L04m3pfix_004c_2", "L06g", "L11", "L03d", 
                 "121_3a_linear_error", "L08d_a", "L03", 
                 "84", "L03_p", "L03b", "L17", 
                 "53_02", "19")
```

## Run Caseum VPCs
```{r}
#### re-run original drug and run list names first

p_case_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_case <- runnos_case[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
p_case <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                           wd,
                                           'Caseum/',
                                           'vpc_',
                                           'run', 
                                           runno_case),
                       obs_cols = list(idv = "TAD"),
                       sim_cols = list(idv = "TAD"),
                       bins = ifelse(drug == "DLM", "none", "pretty"), ## only one bin for DLM
                       pred_corr = F,
                       show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Caseum",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

p_case_plot_list[[i]] <- p_case
}

for (i in seq_along(p_case_plot_list)) {
  print(p_case_plot_list[[i]])
}
```

### DLM, RBT, RZL (using TIME instead of TAD)
```{r}
drugs <- c("DLM", "RBT", "RZL")
wd_values <- c("DLM/Caseum/", "RBT/Caseum/", "RZL/Caseum/")
runnos_case <- c("L03c_v2", "L03_v2", "L24")

p_case_dlm_rbt_rzl_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_case <- runnos_case[i]
  
p_case_dlm_rbt_rzl <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                                       wd,
                                                      'vpc_',
                                                      'run', 
                                                       runno_case),
                         obs_cols = list(idv = "TIME"),
                         sim_cols = list(idv = "TIME"),
                         bins = "pretty",
                         pred_corr = F,
                         show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(24,168,48)) +
  labs(title = "", subtitle = "Caseum",
       x = "Time (h)",
       y = "Concentration (mg/L)")

p_case_dlm_rbt_rzl_list[[i]] <- p_case_dlm_rbt_rzl
}

for (i in seq_along(p_case_dlm_rbt_rzl_list)) {
  print(p_case_dlm_rbt_rzl_list[[i]])
}
```

# :: Arrange plots
```{r}
a <- grid.arrange(p_plasma_plot_list[[1]], p_lung_plot_list[[1]], p_cell_plot_list[[1]], p_case_plot_list[[1]],
                  p_plasma_plot_list[[2]], p_lung_plot_list[[2]], p_cell_plot_list[[2]], p_case_plot_list[[2]],
                  p_plasma_dlm_rbt_rzl_list[[1]], p_lung_dlm_rbt_list[[1]], p_cell_dlm_rbt_list[[1]], p_case_dlm_rbt_rzl_list[[1]], 
                  p_plasma_plot_list[[3]], p_lung_plot_list[[3]], p_cell_plot_list[[3]], p_case_plot_list[[3]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "btz_cfz_dlm_286.png"), plot = a, width = 15, height = 12)

b <- grid.arrange(p_plasma_plot_list[[4]], p_lung_plot_list[[4]], p_cell_plot_list[[4]], p_case_plot_list[[4]],
                  p_plasma_plot_list[[5]], p_lung_plot_list[[5]], p_cell_plot_list[[5]], p_case_plot_list[[5]],
                  p_plasma_plot_list[[6]], p_lung_plot_list[[6]], p_cell_plot_list[[6]], p_case_plot_list[[6]],
                  p_plasma_plot_list[[7]], p_lung_plot_list[[7]], p_cell_plot_list[[7]], p_case_plot_list[[7]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "gfb_gtx_inh_tbd.png"), plot = b, width = 15, height = 12)

c <- grid.arrange(p_plasma_plot_list[[8]], p_lung_plot_list[[8]], p_cell_plot_list[[8]], p_case_plot_list[[8]],
                  p_plasma_plot_list[[9]], p_lung_plot_list[[9]], p_cell_plot_list[[9]], p_case_plot_list[[9]],
                  p_plasma_plot_list[[10]], p_lung_plot_list[[10]], p_cell_plot_list[[10]], p_case_plot_list[[10]],
                  p_plasma_plot_list[[11]], p_lung_plot_list[[11]], p_cell_plot_list[[11]], p_case_plot_list[[11]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "mxf_qbd_pmd_pza.png"), plot = c, width = 15, height = 12)

d <- grid.arrange(p_plasma_dlm_rbt_rzl_list[[2]], p_lung_dlm_rbt_list[[2]], p_cell_dlm_rbt_list[[2]], p_case_dlm_rbt_rzl_list[[2]],
                  p_plasma_plot_list[[12]], p_lung_plot_list[[12]], p_cell_plot_list[[12]], p_case_plot_list[[12]],
                  p_plasma_plot_list[[13]], p_lung_plot_list[[13]], p_cell_plot_list[[13]], p_case_plot_list[[13]],
                  p_plasma_dlm_rbt_rzl_list[[3]], p_lung_rzl_list[[1]], p_cell_rzl_list[[1]], p_case_dlm_rbt_rzl_list[[3]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "rbt_rif_rpt_rzl.png"), plot = d, width = 15, height = 12)
```

# Plasma VPCs (with metabolite)
> BDQ, SZD, TBAJ-587, TBAJ-876

## Gather info for loop
```{r}
drugs <- c("BDQ", "BDQ-M2", "SZD", "SZD-M1", "TBAJ-587", "TBAJ-587-M3", "TBAJ-876", "TBAJ-876-M3")
wd_values <- c("BDQ/Plasma/", "SZD/Plasma/", "TBAJ587/Plasma/", "TBAJ876/Plasma/")
runno_values <- c("59", "73", "61", "134")
```

## Adjust data for cohesion
```{r}
obs_bdq <- read_nm_table(paste0(WD, wd_values[1], 'run', runno_values[1], 'vpc-idv', '/m1/vpc_original.npctab.dta')) %>% filter(METAB==0)
obs_bdq_m2 <- read_nm_table(paste0(WD, wd_values[1], 'run', runno_values[1], 'vpc-idv', '/m1/vpc_original.npctab.dta')) %>% filter(METAB==1)
obs_szd <- read_nm_table(paste0(WD, wd_values[2], 'run', runno_values[2], 'vpc-idv', '/m1/vpc_original.npctab.dta')) %>% filter(METAB==1)
obs_szd_m1 <- read_nm_table(paste0(WD, wd_values[2], 'run', runno_values[2], 'vpc-idv', '/m1/vpc_original.npctab.dta')) %>% filter(METAB==2)
obs_587 <- read_nm_table(paste0(WD, wd_values[3], 'run', runno_values[3], 'vpc-idv', '/m1/vpc_original.npctab.dta')) %>% filter(METAB==0)
obs_587_m3 <- read_nm_table(paste0(WD, wd_values[3], 'run', runno_values[3], 'vpc-idv', '/m1/vpc_original.npctab.dta')) %>% filter(METAB==1)
obs_876 <- read_nm_table(paste0(WD, wd_values[4], 'run', runno_values[4], 'vpc-idv', '/m1/vpc_original.npctab.dta')) %>% filter(CMPD==1)
obs_876_m3 <- read_nm_table(paste0(WD, wd_values[4], 'run', runno_values[4], 'vpc-idv', '/m1/vpc_original.npctab.dta')) %>% filter(CMPD==2)

sim_bdq <- read_nm_table(paste0(WD, wd_values[1], 'run', runno_values[1], 'vpc-idv', '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==0)
sim_bdq_m2 <- read_nm_table(paste0(WD, wd_values[1], 'run', runno_values[1], 'vpc-idv', '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==1)
sim_szd <- read_nm_table(paste0(WD, wd_values[2], 'run', runno_values[2], 'vpc-idv', '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==1)
sim_szd_m1 <- read_nm_table(paste0(WD, wd_values[2], 'run', runno_values[2], 'vpc-idv', '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==2)
sim_587 <- read_nm_table(paste0(WD, wd_values[3], 'run', runno_values[3], 'vpc-idv', '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==0)
sim_587_m3 <- read_nm_table(paste0(WD, wd_values[3], 'run', runno_values[3], 'vpc-idv', '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==1)
sim_876 <- read_nm_table(paste0(WD, wd_values[4], 'run', runno_values[4], 'vpc-idv', '/m1/vpc_simulation.1.npctab.dta')) %>% filter(CMPD==1)
sim_876_m3 <- read_nm_table(paste0(WD, wd_values[4], 'run', runno_values[4], 'vpc-idv', '/m1/vpc_simulation.1.npctab.dta')) %>% filter(CMPD==2)

obs <- list(obs_bdq, obs_bdq_m2, obs_szd, obs_szd_m1, obs_587, obs_587_m3, obs_876, obs_876_m3)
sim <- list(sim_bdq, sim_bdq_m2, sim_szd, sim_szd_m1, sim_587, sim_587_m3, sim_876, sim_876_m3)
```

## Run VPCs
```{r}
pm_plasma_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
pm_plasma <- vpc::vpc_vpc(obs = obs[[i]],
                          sim = sim[[i]],
                          obs_cols = list(idv = "TAD"),
                          sim_cols = list(idv = "TAD"),
                          bins = "pretty",
                          pred_corr = F,
                          show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = drug, subtitle = "Plasma",
       x = "Time after dose (h)",
       y = "Concentration (mg/L)")
pm_plasma_plot_list[[i]] <- pm_plasma
}

for (i in seq_along(pm_plasma_plot_list)) {
  print(pm_plasma_plot_list[[i]])
}
```

# Lesion VPCs (with metabolite)
> BDQ, SZD, TBAJ-587, TBAJ-876

# **Jointly modeled

### Gather info for loop
```{r}
drugs <- c("SZD", "SZD-M1", "TBAJ-876", "TBAJ-876-M3")
wd_values <- c("SZD/", "TBAJ876/")
runnos_lung <- c("27", "L33")
runnos_cell <- c("30", "L32")
runnos_case <- c("31", "L31")
```

### Adjust data for cohesion
```{r}
obs_szd <- read_nm_table(paste0(WD, wd_values[1], 'Lung/vpc_run', runnos_lung[1], '/m1/vpc_original.npctab.dta')) %>% filter(METAB==1)
obs_szd_m1 <- read_nm_table(paste0(WD, wd_values[1], 'Lung/vpc_run', runnos_lung[1], '/m1/vpc_original.npctab.dta')) %>% filter(METAB==2)
obs_876 <- read_nm_table(paste0(WD, wd_values[2], 'Lung/vpc_run', runnos_lung[2], '/m1/vpc_original.npctab.dta')) %>% filter(CMPD==1)
obs_876_m3 <- read_nm_table(paste0(WD, wd_values[2], 'Lung/vpc_run', runnos_lung[2], '/m1/vpc_original.npctab.dta')) %>% filter(CMPD==2)

sim_szd <- read_nm_table(paste0(WD, wd_values[1], 'Lung/vpc_run', runnos_lung[1], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==1)
sim_szd_m1 <- read_nm_table(paste0(WD, wd_values[1], 'Lung/vpc_run', runnos_lung[1], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==2)
sim_876 <- read_nm_table(paste0(WD, wd_values[2], 'Lung/vpc_run', runnos_lung[2], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(CMPD==1)
sim_876_m3 <- read_nm_table(paste0(WD, wd_values[2], 'Lung/vpc_run', runnos_lung[2], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(CMPD==2)

obs <- list(obs_szd, obs_szd_m1, obs_876, obs_876_m3)
sim <- list(sim_szd, sim_szd_m1, sim_876, sim_876_m3)
```

#### Run Lung VPCs
```{r}
pm_lung_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]

options(repr.plot.width = 6, repr.plot.height = 4)
pm_lung <- vpc::vpc_vpc(obs = obs[[i]],
                        sim = sim[[i]],
                        obs_cols = list(idv = "TAD"),
                        sim_cols = list(idv = "TAD"),
                        bins = "pretty",
                        pred_corr = F,
                        show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Lung",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

pm_lung_plot_list[[i]] <- pm_lung
}

for (i in seq_along(pm_lung_plot_list)) {
  print(pm_lung_plot_list[[i]])
}
```

### Adjust data for cohesion
```{r}
obs_szd <- read_nm_table(paste0(WD, wd_values[1], 'Cell/vpc_run', runnos_cell[1], '/m1/vpc_original.npctab.dta')) %>% filter(METAB==1)
obs_szd_m1 <- read_nm_table(paste0(WD, wd_values[1], 'Cell/vpc_run', runnos_cell[1], '/m1/vpc_original.npctab.dta')) %>% filter(METAB==2)
obs_876 <- read_nm_table(paste0(WD, wd_values[2], 'Cell/vpc_run', runnos_cell[2], '/m1/vpc_original.npctab.dta')) %>% filter(CMPD==1)
obs_876_m3 <- read_nm_table(paste0(WD, wd_values[2], 'Cell/vpc_run', runnos_cell[2], '/m1/vpc_original.npctab.dta')) %>% filter(CMPD==2)

sim_szd <- read_nm_table(paste0(WD, wd_values[1], 'Cell/vpc_run', runnos_cell[1], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==1)
sim_szd_m1 <- read_nm_table(paste0(WD, wd_values[1], 'Cell/vpc_run', runnos_cell[1], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==2)
sim_876 <- read_nm_table(paste0(WD, wd_values[2], 'Cell/vpc_run', runnos_cell[2], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(CMPD==1)
sim_876_m3 <- read_nm_table(paste0(WD, wd_values[2], 'Cell/vpc_run', runnos_cell[2], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(CMPD==2)

obs <- list(obs_szd, obs_szd_m1, obs_876, obs_876_m3)
sim <- list(sim_szd, sim_szd_m1, sim_876, sim_876_m3)
```

#### Run Cell VPCs
```{r}
pm_cell_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
pm_cell <- vpc::vpc_vpc(obs = obs[[i]],
                        sim = sim[[i]],
                        obs_cols = list(idv = "TAD"),
                        sim_cols = list(idv = "TAD"),
                        bins = "pretty",
                        pred_corr = F,
                        show = list(obs_dv =T, obs_ci = F,pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Cellular Lesion",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

pm_cell_plot_list[[i]] <- pm_cell
}

for (i in seq_along(pm_cell_plot_list)) {
  print(pm_cell_plot_list[[i]])
}
```

### Adjust data for cohesion
```{r}
obs_szd <- read_nm_table(paste0(WD, wd_values[1], 'Caseum/vpc_run', runnos_case[1], '/m1/vpc_original.npctab.dta')) %>% filter(METAB==1)
obs_szd_m1 <- read_nm_table(paste0(WD, wd_values[1], 'Caseum/vpc_run', runnos_case[1], '/m1/vpc_original.npctab.dta')) %>% filter(METAB==2)
obs_876 <- read_nm_table(paste0(WD, wd_values[2], 'Caseum/vpc_run', runnos_case[2], '/m1/vpc_original.npctab.dta')) %>% filter(CMPD==1)
obs_876_m3 <- read_nm_table(paste0(WD, wd_values[2], 'Caseum/vpc_run', runnos_case[2], '/m1/vpc_original.npctab.dta')) %>% filter(CMPD==2)

sim_szd <- read_nm_table(paste0(WD, wd_values[1], 'Caseum/vpc_run', runnos_case[1], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==1)
sim_szd_m1 <- read_nm_table(paste0(WD, wd_values[1], 'Caseum/vpc_run', runnos_case[1], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(METAB==2)
sim_876 <- read_nm_table(paste0(WD, wd_values[2], 'Caseum/vpc_run', runnos_case[2], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(CMPD==1)
sim_876_m3 <- read_nm_table(paste0(WD, wd_values[2], 'Caseum/vpc_run', runnos_case[2], '/m1/vpc_simulation.1.npctab.dta')) %>% filter(CMPD==2)

obs <- list(obs_szd, obs_szd_m1, obs_876, obs_876_m3)
sim <- list(sim_szd, sim_szd_m1, sim_876, sim_876_m3)
```

#### Run Caseum VPCs
```{r}
pm_case_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
pm_case <- vpc::vpc_vpc(obs = obs[[i]],
                        sim = sim[[i]],
                        obs_cols = list(idv = "TAD"),
                        sim_cols = list(idv = "TAD"),
                        bins = "pretty",
                        pred_corr = F,
                        show = list(obs_dv =T, obs_ci = F,pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Caseum",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

pm_case_plot_list[[i]] <- pm_case
}

for (i in seq_along(pm_case_plot_list)) {
  print(pm_case_plot_list[[i]])
}
```

# :: Arrange plots
```{r}
# plasma plots match SZD, SZD-M1, TBAJ-876, TBAJ-876-M3
g <- grid.arrange(pm_plasma_plot_list[[3]], pm_lung_plot_list[[1]], pm_cell_plot_list[[1]], pm_case_plot_list[[1]],
                  pm_plasma_plot_list[[4]], pm_lung_plot_list[[2]], pm_cell_plot_list[[2]], pm_case_plot_list[[2]],
                  pm_plasma_plot_list[[7]], pm_lung_plot_list[[3]], pm_cell_plot_list[[3]], pm_case_plot_list[[3]],
                  pm_plasma_plot_list[[8]], pm_lung_plot_list[[4]], pm_cell_plot_list[[4]], pm_case_plot_list[[4]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "szd_876_plus_metab.png"), plot = g, width = 15, height = 12)
```

# ** Separately modeled

### Gather info for loop
```{r}
drugs <- c("BDQ", "BDQ-M2", "TBAJ-587", "TBAJ-587-M3")
wd_values <- c("BDQ/Parent/", "BDQ/Metab/", "TBAJ587/Parent/", "TBAJ587/Metab/")
runnos_lung <- c("L01d", "L01e", "L06", "L06b")
runnos_cell <- c("L02a", "L02b", "L04b", "L04e")
runnos_case <- c("L05b", "L06a", "L02b4", "L07")
```

### Run Lung VPCs
```{r}
pms_lung_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_lung <- runnos_lung[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
pms_lung <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                             wd,
                                             'Lung/',
                                             'vpc_',
                                             'run', 
                                             runno_lung),
                       obs_cols = list(idv = "TAD"),
                       sim_cols = list(idv = "TAD"),
                       bins = "pretty",
                       pred_corr = F,
                       show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Lung",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

pms_lung_plot_list[[i]] <- pms_lung
}

for (i in seq_along(pms_lung_plot_list)) {
  print(pms_lung_plot_list[[i]])
}
```

### Run Cell VPCs
```{r}
pms_cell_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_cell <- runnos_cell[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
pms_cell <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                             wd,
                                             'Cell/',
                                             'vpc_',
                                             'run', 
                                             runno_cell),
                       obs_cols = list(idv = "TAD"),
                       sim_cols = list(idv = "TAD"),
                       bins = "pretty",
                       pred_corr = F,
                       show = list(obs_dv = T, obs_ci = F, pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Cellular Lesion",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

pms_cell_plot_list[[i]] <- pms_cell
}

for (i in seq_along(pms_cell_plot_list)) {
  print(pms_cell_plot_list[[i]])
}
```

### Run Caseum VPCs
```{r}
pms_case_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_case <- runnos_case[i]
  
options(repr.plot.width = 6, repr.plot.height = 4)
pms_case <- vpc::vpc_vpc(psn_folder = paste0(WD, 
                                             wd,
                                             'Caseum/',
                                             'vpc_',
                                             'run', 
                                             runno_case),
                       obs_cols = list(idv = "TAD"),
                       sim_cols = list(idv = "TAD"),
                       bins = "pretty",
                       pred_corr = F,
                       show = list(obs_dv = T, obs_ci = F,pi = T, pi_as_area = T)) +
  theme_bw(base_size = 16) +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks = seq(0,120,12)) +
  labs(title = "", subtitle = "Caseum",
       x = "Time after dose (h)",
       y = "Concentration (mg/kg)")

pms_case_plot_list[[i]] <- pms_case
}

for (i in seq_along(pms_case_plot_list)) {
  print(pms_case_plot_list[[i]])
}
```

# :: Arrange plots
```{r}
# plasma plots match BDQ, BDQ-M2, TBAJ-587, TBAJ-587-M3
h <- grid.arrange(pm_plasma_plot_list[[1]], pms_lung_plot_list[[1]], pms_cell_plot_list[[1]], pms_case_plot_list[[1]],
                  pm_plasma_plot_list[[2]], pms_lung_plot_list[[2]], pms_cell_plot_list[[2]], pms_case_plot_list[[2]],
                  pm_plasma_plot_list[[5]], pms_lung_plot_list[[3]], pms_cell_plot_list[[3]], pms_case_plot_list[[3]],
                  pm_plasma_plot_list[[6]], pms_lung_plot_list[[4]], pms_cell_plot_list[[4]], pms_case_plot_list[[4]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "bdq_587_plus_metab.png"), plot = h, width = 15, height = 12)
```
