---
title: "Lesion manuscript - Rabbit model GoF plots for all drugs"
author: "Anu Patel"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Set Up
```{r setup, include=FALSE}
library(vpc)
library(xpose)
library(xpose4)
library(grid)
library(gridExtra)
library(ggplot2)
library(reshape)

# master path
WD <- "/Volumes/savic/translational_team/aebustion/lesion_gofs/"
```

# Plasma (no metabolite)
> BTZ-043, CFZ, DLM, GSK-286, GSK-656 (GFB), GTX, INH, mCLB-073 (TBD-11), MXF, OPC-167832 (QBD), PMD, PZA, RBT, RIF, RPT, RZL

## Gather info for loop
```{r}
drugs <- c("BTZ-043", "CFZ", "DLM", "GSK-286",
           "GFB", "GTX", "INH", "TBD-11", 
           "MXF", "QBD", "PMD", "PZA", 
           "RBT", "RIF", "RPT", "RZL")

wd_values <- c("BTZ043/", "CFZ/", "DLM/", "GSK286/",
               "GSK656/", "GTX/", "INH/", "mCLB073/", 
               "MXF/", "OPC167832/", "PMD/", "PZA/", 
               "RBT/", "RIF/", "RPT/", "RZL/")

runno_values <- c("004c", "11b",  "29", "30",
                  "100", "121_CLint", "07", "20", 
                  "31", "9", "13", "04", 
                  "15", "02", "6", "46")
```

## Run GoF plots
```{r}
p_plasma_plot_list <- list() # create an empty list to store the plots

for (i in seq_along(drugs)) { # to access corresponding elements of each list for each loop
  drug <- drugs[i]
  wd <- wd_values[i]
  runno <- runno_values[i]
  
setwd(paste0(WD, wd))
xpdb <- xpose_data(runno = runno)

options(repr.plot.width = 6, repr.plot.height = 4)
p_plasma <- dv_vs_ipred(xpdb, 
                        guide = T, 
                        type = "pl",
                        caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = drug, subtitle = "Plasma",
       x = "Individual predictions",
       y = "Observations")

p_plasma_plot_list[[i]] <- p_plasma # store each plot in the list
}

for (i in seq_along(p_plasma_plot_list)) { # display each plot
  print(p_plasma_plot_list[[i]])
}
```

# Lesion (no metabolite)
> BTZ-043, CFZ, DLM, GSK-286, GSK-656 (GFB), GTX, INH, mCLB-073 (TBD-11), MXF, OPC-167832 (QBD), PMD, PZA, RBT, RIF, RPT, RZL

## Gather info for loop
```{r}
drugs <- c("BTZ-043", "CFZ", "DLM", "GSK-286",
           "GFB", "GTX", "INH", "TBD-11", 
           "MXF", "QBD", "PMD", "PZA", 
           "RBT", "RIF", "RPT", "RZL")

wd_values <- c("BTZ043/", "CFZ/", "DLM/", "GSK286/",
               "GSK656/", "GTX/", "INH/", "mCLB073/",
               "MXF/", "OPC167832/", "PMD/", "PZA/",
               "RBT/", "RIF/", "RPT/", "RZL/")

runnos_lung <- c("L01p_004c", "L01b", "L01b", "L14", 
                 "L01c", "121_1a_linear_error", "L01", "L08", 
                 "54b_p", "L02_pfix", "L01", "L10", 
                 "L01", "46_02", "11", "L22")

runnos_cell <- c("L02p_004c", "L02b", "L02g", "L13", 
                 "L02d", "121_2a_linear_error", "L02", "L07", 
                 "64", "L01_pfix", "L02a", "L13", 
                 "L02", "52_02", "18", "L23")

runnos_case <- c("L04m3pfix_004c_2", "L06g", "L03c", "L11",
                 "L03d", "121_3a_linear_error", "L08d_a", "L03", 
                 "84", "L03_p", "L03b", "L17", 
                 "L03", "53_02", "19", "L24")
```

## Run Lung GoF plots
```{r}
p_lung_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_lung <- runnos_lung[i]
  
setwd(paste0(WD, wd))
xpdb <- xpose_data(runno = runno_lung)

options(repr.plot.width = 6, repr.plot.height = 4)
p_lung <- dv_vs_ipred(xpdb, 
                      guide = T, 
                      type = "pl",
                      caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = "", subtitle = "Lung",
       x = "Individual predictions",
       y = "Observations")
p_lung 

p_lung_plot_list[[i]] <- p_lung
}

for (i in seq_along(p_lung_plot_list)) {
  print(p_lung_plot_list[[i]])
}
```

## Run Cell GoF plots
```{r}
p_cell_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_cell <- runnos_cell[i]
  
setwd(paste0(WD, wd))
xpdb <- xpose_data(runno = runno_cell)

options(repr.plot.width = 6, repr.plot.height = 4)
p_cell <- dv_vs_ipred(xpdb, 
                      guide = T, 
                      type = "pl",
                      caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = "", subtitle = "Cellular Lesion",
       x = "Individual predictions",
       y = "Observations")

p_cell_plot_list[[i]] <- p_cell
}

for (i in seq_along(p_cell_plot_list)) {
  print(p_cell_plot_list[[i]])
}
```

## Run Caseum GoF plots
```{r}
p_case_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_case <- runnos_case[i]
  
setwd(paste0(WD, wd))
xpdb <- xpose_data(runno = runno_case)

options(repr.plot.width = 6, repr.plot.height = 4)
p_case <- dv_vs_ipred(xpdb, 
                      guide = T, 
                      type = "pl",
                      caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = "", subtitle = "Caseum",
       x = "Individual predictions",
       y = "Observations")

p_case_plot_list[[i]] <- p_case
}

for (i in seq_along(p_case_plot_list)) {
  print(p_case_plot_list[[i]])
}
```

# :: Arrange plots
```{r}
a <- grid.arrange(p_plasma_plot_list[[1]], p_lung_plot_list[[1]], p_cell_plot_list[[1]], p_case_plot_list[[1]],
                  p_plasma_plot_list[[2]], p_lung_plot_list[[2]], p_cell_plot_list[[2]], p_case_plot_list[[2]],
                  p_plasma_plot_list[[3]], p_lung_plot_list[[3]], p_cell_plot_list[[3]], p_case_plot_list[[3]],
                  p_plasma_plot_list[[5]], p_lung_plot_list[[5]], p_cell_plot_list[[5]], p_case_plot_list[[5]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "btz_cfz_dlm_gfb.png"), plot = a, width = 15, height = 12)

b <- grid.arrange(p_plasma_plot_list[[4]], p_lung_plot_list[[4]], p_cell_plot_list[[4]], p_case_plot_list[[4]],
                  p_plasma_plot_list[[6]], p_lung_plot_list[[6]], p_cell_plot_list[[6]], p_case_plot_list[[6]],
                  p_plasma_plot_list[[7]], p_lung_plot_list[[7]], p_cell_plot_list[[7]], p_case_plot_list[[7]],
                  p_plasma_plot_list[[9]], p_lung_plot_list[[9]], p_cell_plot_list[[9]], p_case_plot_list[[9]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "286_gtx_inh_mxf.png"), plot = b, width = 15, height = 12)

c <- grid.arrange(p_plasma_plot_list[[11]], p_lung_plot_list[[11]], p_cell_plot_list[[11]], p_case_plot_list[[11]],
                  p_plasma_plot_list[[12]], p_lung_plot_list[[12]], p_cell_plot_list[[12]], p_case_plot_list[[12]],
                  p_plasma_plot_list[[10]], p_lung_plot_list[[10]], p_cell_plot_list[[10]], p_case_plot_list[[10]],
                  p_plasma_plot_list[[13]], p_lung_plot_list[[13]], p_cell_plot_list[[13]], p_case_plot_list[[13]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "pmd_pza_qbd_rbt.png"), plot = c, width = 15, height = 12)

d <- grid.arrange(p_plasma_plot_list[[14]], p_lung_plot_list[[14]], p_cell_plot_list[[14]], p_case_plot_list[[14]],
                  p_plasma_plot_list[[15]], p_lung_plot_list[[15]], p_cell_plot_list[[15]], p_case_plot_list[[15]],
                  p_plasma_plot_list[[16]], p_lung_plot_list[[16]], p_cell_plot_list[[16]], p_case_plot_list[[16]],
                  p_plasma_plot_list[[8]], p_lung_plot_list[[8]], p_cell_plot_list[[8]], p_case_plot_list[[9]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "rif_rpt_rzl_tbd.png"), plot = d, width = 15, height = 12)
```

# Plasma (with metabolite)
> BDQ, SZD, TBAJ587, TBAJ876

## Gather info for loop
```{r}
drugs <- c("BDQ", "BDQ-M2", "SZD", "SZD-M1", "TBAJ-587", "TBAJ-587-M3", "TBAJ-876", "TBAJ-876-M3")
wd_values <- c("BDQ/", "SZD/", "TBAJ587/", "TBAJ876/")
runno_values <- c("59", "73", "61", "134")
```

## Adjust data for cohesion
```{r}
# BDQ
setwd(paste0(WD, wd_values[1]))
bdq <- xpose_data(runno = runno_values[1])
xpdb_bdq <- filter(bdq, METAB==0)
xpdb_bdq_m2 <- filter(bdq, METAB==1)
# SZD
setwd(paste0(WD, wd_values[2]))
szd <- xpose_data(runno = runno_values[2])
xpdb_szd <- filter(szd, METAB==1)
xpdb_szd_m1 <- filter(szd, METAB==2)
# TBAJ-587
setwd(paste0(WD, wd_values[3]))
s587 <- xpose_data(runno = runno_values[3])
xpdb_587 <- filter(s587, METAB==0)
xpdb_587_m3 <- filter(s587, METAB==1)
# TBAJ-876
setwd(paste0(WD, wd_values[4]))
s876 <- xpose_data(runno = runno_values[4])
xpdb_876 <- filter(s876, CMPD==1)
xpdb_876_m3 <- filter(s876, CMPD==2)

xpdb_all <- list(xpdb_bdq, xpdb_bdq_m2, xpdb_szd, xpdb_szd_m1, xpdb_587, xpdb_587_m3, xpdb_876, xpdb_876_m3)
```

## Run GoF plots
```{r}
pm_plasma_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  xpdb <- xpdb_all[[i]]

options(repr.plot.width = 6, repr.plot.height = 4)
pm_plasma <- dv_vs_ipred(xpdb, 
                         guide = T, 
                         type = "pl",
                         caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = drug, subtitle = "Plasma",
       x = "Individual predictions",
       y = "Observations")

pm_plasma_plot_list[[i]] <- pm_plasma
}

for (i in seq_along(pm_plasma_plot_list)) {
  print(pm_plasma_plot_list[[i]])
}
```

# Lesion (with metabolite)
> BDQ, SZD, TBAJ-587, TBAJ-876

# **Jointly modeled (just SZD)

### Gather info for loop
```{r}
drugs <- c("SZD", "SZD-M1")
wd <- "SZD/"
runno_lung <- "27"
runno_cell <- "30"
runno_case <- "31"
```

### Adjust data for cohesion
```{r}
# SZD
setwd(paste0(WD, wd))
szd <- xpose_data(runno = runno_lung)
xpdb_szd <- filter(szd, METAB==1)
xpdb_szd_m1 <- filter(szd, METAB==2)

xpdb_all <- list(xpdb_szd, xpdb_szd_m1)
```

#### Run Lung GoF plots
```{r}
pm_lung_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  xpdb <- xpdb_all[[i]]

options(repr.plot.width = 6, repr.plot.height = 4)
pm_lung <- dv_vs_ipred(xpdb, 
                       guide = T, 
                       type = "pl",
                       caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = "", subtitle = "Lung",
       x = "Individual predictions",
       y = "Observations")

pm_lung_plot_list[[i]] <- pm_lung
}

for (i in seq_along(pm_lung_plot_list)) {
  print(pm_lung_plot_list[[i]])
}
```

### Adjust data for cohesion
```{r}
# SZD
setwd(paste0(WD, wd))
szd <- xpose_data(runno = runno_cell)
xpdb_szd <- filter(szd, METAB==1)
xpdb_szd_m1 <- filter(szd, METAB==2)

xpdb_all <- list(xpdb_szd, xpdb_szd_m1)
```

#### Run Cell GoF plots
```{r}
pm_cell_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  xpdb <- xpdb_all[[i]]

options(repr.plot.width = 6, repr.plot.height = 4)
pm_cell <- dv_vs_ipred(xpdb, 
                       guide = T, 
                       type = "pl",
                       caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = "", subtitle = "Cellular Lesion",
       x = "Individual predictions",
       y = "Observations")

pm_cell_plot_list[[i]] <- pm_cell
}

for (i in seq_along(pm_cell_plot_list)) {
  print(pm_cell_plot_list[[i]])
}
```

### Adjust data for cohesion
```{r}
# SZD
setwd(paste0(WD, wd))
szd <- xpose_data(runno = runno_case)
xpdb_szd <- filter(szd, METAB==1)
xpdb_szd_m1 <- filter(szd, METAB==2)

xpdb_all <- list(xpdb_szd, xpdb_szd_m1)
```

#### Run Caseum VPCs
```{r}
pm_case_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  xpdb <- xpdb_all[[i]]

options(repr.plot.width = 6, repr.plot.height = 4)
pm_case <- dv_vs_ipred(xpdb, 
                       guide = T, 
                       type = "pl",
                       caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = "", subtitle = "Caseum",
       x = "Individual predictions",
       y = "Observations")

pm_case_plot_list[[i]] <- pm_case
}

for (i in seq_along(pm_case_plot_list)) {
  print(pm_case_plot_list[[i]])
}
```

# ** Separately modeled

### Gather info for loop
```{r}
drugs <- c("BDQ", "BDQ-M2", "TBAJ-587", "TBAJ-587-M3", "TBAJ-876", "TBAJ-876-M3")
wd_values <- c("BDQ/", "BDQ/", "TBAJ587/", "TBAJ587/", "TBAJ876/", "TBAJ876/")
runnos_lung <- c("L01d", "L01e", "L06", "L06b", "L29", "L30")
runnos_cell <- c("L02a", "L02b", "L04b", "L04e", "L27", "L28")
runnos_case <- c("L05b", "L06a", "L02b4", "L07", "L25", "L26")
```

### Run Lung GoF plots
```{r}
pms_lung_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_lung <- runnos_lung[i]
  
setwd(paste0(WD, wd))
xpdb <- xpose_data(runno = runno_lung)

options(repr.plot.width = 6, repr.plot.height = 4)
pms_lung <- dv_vs_ipred(xpdb, 
                        guide = T, 
                        type = "pl",
                        caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = "", subtitle = "Lung",
       x = "Individual predictions",
       y = "Observations")

pms_lung_plot_list[[i]] <- pms_lung
}

for (i in seq_along(pms_lung_plot_list)) {
  print(pms_lung_plot_list[[i]])
}
```

### Run Cell GoF plots
```{r}
pms_cell_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_cell <- runnos_cell[i]
  
setwd(paste0(WD, wd))
xpdb <- xpose_data(runno = runno_cell)

options(repr.plot.width = 6, repr.plot.height = 4)
pms_cell <- dv_vs_ipred(xpdb, 
                        guide = T, 
                        type = "pl",
                        caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = "", subtitle = "Cellular Lesion",
       x = "Individual predictions",
       y = "Observations")

pms_cell_plot_list[[i]] <- pms_cell
}

for (i in seq_along(pms_cell_plot_list)) {
  print(pms_cell_plot_list[[i]])
}
```

### Run Caseum GoF plots
```{r}
pms_case_plot_list <- list()

for (i in seq_along(drugs)) {
  drug <- drugs[i]
  wd <- wd_values[i]
  runno_case <- runnos_case[i]
  
setwd(paste0(WD, wd))
xpdb <- xpose_data(runno = runno_case)

options(repr.plot.width = 6, repr.plot.height = 4)
pms_case <- dv_vs_ipred(xpdb, 
                        guide = T, 
                        type = "pl",
                        caption = NULL) +
  theme_bw(base_size = 16) +
  labs(title = "", subtitle = "Caseum",
       x = "Individual predictions",
       y = "Observations")

pms_case_plot_list[[i]] <- pms_case
}

for (i in seq_along(pms_case_plot_list)) {
  print(pms_case_plot_list[[i]])
}
```


# :: Arrange plots
```{r}
# BDQ, BDQ-M2, SZD, SZD-M1
f <- grid.arrange(pm_plasma_plot_list[[1]], pms_lung_plot_list[[1]], pms_cell_plot_list[[1]], pms_case_plot_list[[1]],
                  pm_plasma_plot_list[[2]], pms_lung_plot_list[[2]], pms_cell_plot_list[[2]], pms_case_plot_list[[2]],
                  pm_plasma_plot_list[[3]], pm_lung_plot_list[[1]], pm_cell_plot_list[[1]], pm_case_plot_list[[1]],
                  pm_plasma_plot_list[[4]], pm_lung_plot_list[[2]], pm_cell_plot_list[[2]], pm_case_plot_list[[2]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "bdq_szd_plus_metab.png"), plot = f, width = 15, height = 12)

# TBAJ-587, TBAJ-587-M3, TBAJ-876, TBAJ-876-M3
g <- grid.arrange(pm_plasma_plot_list[[5]], pms_lung_plot_list[[3]], pms_cell_plot_list[[3]], pms_case_plot_list[[3]],
                  pm_plasma_plot_list[[6]], pms_lung_plot_list[[4]], pms_cell_plot_list[[4]], pms_case_plot_list[[4]],
                  pm_plasma_plot_list[[7]], pms_lung_plot_list[[5]], pms_cell_plot_list[[5]], pms_case_plot_list[[5]],
                  pm_plasma_plot_list[[8]], pms_lung_plot_list[[6]], pms_cell_plot_list[[6]], pms_case_plot_list[[6]],
                  ncol = 4)
ggsave(paste0(WD, 'Plots/', "587_876_plus_metab.png"), plot = g, width = 15, height = 12)
```
